Seismic parameter estimation and the Canadian crust

### 2013-07-26 paper/draftBP.tex
conrad

\subsection{Full Parameter Search Analysis}
Comparing the ZK approach with the full parameter search (Table \ref{table:ZKvsFG}) we see that the velocity ratio $R$ has a correlation between the two datasets of 0.76 while $H$ has a correlation of only 0.51. Since $t_{Ps}$ represents the differential travel time between the S and P wave, the dependence of $H$ on $V_P$ is weak. This means that for a given uncertainty in the three dimensional stack $s(H,R,V_P)$, the gradient in the stack-space will be lowest along the kinematic curve in the $H$ and $V_P$ axis (Figure \ref{fig:HVp_ULM}). This conveys the inherent trade-off in resolution between $H$ and $V_P$ and contributes to the low correlation between the two methods. Parity between the ZK and FG methods can be regained by dividing out $V_P$ from $H$. The trade-off between the other parameters is lower, owing to greater dependence between the parameters in the travel time equations (Figures \ref{fig:HR_ULM}-\ref{fig:RVp_ULM}.

@@

\subsection{Conrad Discontinuity}
Results and figures showing statistics regarding depth of crustal reflectors.
[[ Idea: Statistical test of distributions? How much confidence in a range of modes n = 1->5
   Winning number of modes - partition the dataset for those stations with those modes
   map spatially and see if it is a geographic density bias / trend ]]

>>>>

\subsection{Full Parameter Search Analysis}
Comparing the ZK approach with the full parameter search (Table \ref{table:ZKvsFG}) we see that the velocity ratio $R$ has a correlation between the two datasets of 0.76 while $H$ has a correlation of 0.51. The low correlation between crustal thickness estimates can be explained by the weak dependence of $H$ on $V_P$ resulting from $t_{Ps}$. This means that for a given uncertainty in the three dimensional stack $s(H,R,V_P)$, the gradient in the stack-space will be lowest along the kinematic curve in the $H$ and $V_P$ axis (Figure \ref{fig:HVp_ULM}). This conveys the inherent trade-off in resolution between $H$ and $V_P$ and contributes to the low correlation between the two methods. Parity between the ZK and FG methods can be regained by dividing out $V_P$ from $H$. The trade-off between the other parameters is lower as there is greater dependence between the parameters in the travel time equations (Figures \ref{fig:HR_ULM}-\ref{fig:RVp_ULM}.

@@

\subsection{Crustal Discontinuities}
